---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rtdda

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![MIT Licensed - Copyright 2016 EcoHealth Alliance](https://img.shields.io/badge/license-MIT-blue.svg)](https://badges.mit-license.org/)
[![Travis-CI Build Status](https://travis-ci.org/noamross/rtdda.svg?branch=master)](https://travis-ci.org/noamross/rtdda)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/noamross/rtdda?branch=master&svg=true)](https://ci.appveyor.com/project/noamross/rtdda)

This package wraps the [tdda python module](https://github.com/tdda/tdda),
which generates automatic *constraints* on data sets given examples. More
info can be found on [the TDDA blog](http://www.tdda.info/introducing-rexpy-automatic-discovery-of-regular-expressions).

This is an extremely alpha package wrapping some pretty beta code, so use
with caution!  It does not currently work on Windows.

## Installation

You can install rtdda from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("noamross/rtdda")
```

Since rtdda calls python code via the [**SnakeCharmR**](https://github.com/asieira/SnakeCharmR)
package, you need Python >= 2.7 and a build environment to install it.

## Usage

Currently only one function, `rex_extract()` is implemented, for regular expression generation from a character vector:

```{r example}
library(rtdda)
rex_extract(c("EH1", "7JQ", "WC1", "4AA", "G2", "3PQ"))
rex_extract(c("123-AA-971", "12-DQ-802", "198-AA-045", "1-BA-834"))
```
